\documentclass[11pt,a4paper]{resume}

\cvname{Dwight K.}{Schrute III}
\cvaddress{1 Main Street | Scranton, PA 18503}
\cvmobile{(570) 555-1212}
\cvemail{d.schrute@schrutefarms.com}
\cvhomepage{schrutefarms.com}

\github{dmoney}
\gitlab{dmoney}
\linkedin{dwigt}
\twitter{@DwightARM}
\skype{PaperSalez}

\pagenumbering{gobble}

\newcommand{\content}{
  % \section{Skills}
  \begin{skills}
    \subsection{Traits}
    \begin{programming}
    \item Hardworking
    \item Alpha Male
    \item Jackhammer
    \item Merciless
    \item Insatiable
    \end{programming}
    \subsection{Talents}
    \begin{programming}
    \item Karate (Purple Belt)
    \item Jujitsu
    \item Werewolf hunting
    \item Table Making
    \end{programming}
    \subsection{Languages}
    \begin{languages}
    \item English (Native)
    \item German (Fluent)
    \item Klingon (Intermediate)
    \end{languages}
  \end{skills}

  % \begin{minipage}{.3\linewidth}
  \section{Education}
  \begin{education}
    \degree{
      Scranton University
    }{BA Business Administration}{Scranton, PA}{1992 -- 1998}{
    }
    \degree{
      Cornell University
    }{NA Anger Management}{New York}{S05E06}{
    }
  \end{education}

  \section{Experience}
  \begin{experience}
    \job{Dunder Mifflin}{Regional Manager}{Scranton, PA}{May 2013 -- Present}{
      \begin{tightitemize}
      \item Maintained the highest sales average, despite the weak economy and
        obsolete product.
      \item Managed, inspired, and protected the Scranton branch from criminals
        and raccoons.
      \item Led the office to obtain immeasurable success and glory.
      \end{tightitemize}
    }

    \job{Dunder Mifflin}{Assistant (to the) Regional Manager}{Scranton, PA}{Mar
      2008 -- Mar 2013}{
      \begin{tightitemize}
      \item Closed more sales with revenues totaling more profit than any other
        employee --- past, present, and future (projected).
      \item Served as self-appointed enforcer of The Rules (policies and
        procedures manual).
      \item Instituted \emph{Schrute Bucks} reward system, immeasurably raising
        office morale.
      \end{tightitemize}
    }

    \job{Staples}{Sale's Associate}{Scranton, PA}{Mar 2008}{
      \begin{tightitemize}
      \item Became the top salesman of the store within a one-month timespan.
      \item Made a record-high sales figure despite having an unfunny boss.
      \item Provided extraordinary and exceptional customer service to the masses.
      \end{tightitemize}
    }

    \job{Dunder Mifflin}{Assistant (to the) Regional Manager}{Scranton, PA}{Mar
      2005 -- Mar 2008}{
      \begin{tightitemize}
      \item Acted as Regional Manager's eyes, ears, and right hand, overseeing
        and reporting on employee conduct, productivity, and arrival/departure
        times.
      \item Provided services to the office such as martial arts and surveillance.
      \item Introduced new linen paper lines into the market, often closing
        sight-unseen sales of newly released products.
      \end{tightitemize}
    }
  \end{experience}

  \vspace{-1em}

  \begin{minipage}[t]{.58\linewidth}
    \section{Projects}
    \begin{projects}
      \project{Schrute Farms (Bed \& Breakfast)}{A beautiful resort that
        provides fun activities like table making and mattress making.}
      \project{Dwight Schrute's Gym for Muscles}{A built-in gym inside the
        Dunder Mifflin office that will make you shredded.}
      \project{Sesame Avenue Daycare Center for Infants and Toddlers}{A great
        daycare for infants with a focus on cognitive development.}
    \end{projects}

  \end{minipage}
  \hfill
  \begin{minipage}[t]{.4\linewidth}
    \section{Awards}
    \begin{awards}
      \award{Salesman of the Month}{2013}{13-time award winner}
    \end{awards}
  \end{minipage}
}

\begin{document}
\makeheader
\content

% Variations of black and gray
\newpage
\fillheader{black!80}{white}
\makeheader
\content
\newpage
\fillheader{black}{white}
\makeheader
\content

% Colored headers
% colors are defined in common/colors.tex
\newpage
\fillheader{gunmetal}{white} % defined in common/colors.tex
\makeheader
\content
\newpage
\fillheader{oxford}{white} % defined in common/colors.tex
\makeheader
\content
\newpage
\fillheader{MaastrichtBlue1}{white}
\makeheader
\content
\newpage
\fillheader{MaastrichtBlue2}{white}
\makeheader
\content
\newpage
\fillheader{DarkSienna1}{white}
\makeheader
\content
\newpage
\fillheader{DarkSienna2}{white}
\makeheader
\content
\end{document}
